Fleet Definitions

### 2021-03-01 docs/GBFleetDefinitions.Rmd
bug fix: labels not matching gear types in dendrogram plot

```
```{r dendro1,out.width="100%",fig.cap="The denrogram obtained from a nearest-neighbor, hierarchical cluster analysis on all gears used in the Georges Bank Ecological Production unit defined by statistical areas"}
knitr::include_graphics("figures/dendrogram1.png")
```

>>>>

```
```{r dendro1,out.width="100%",fig.cap="The denrogram obtained from a nearest-neighbor, hierarchical cluster analysis on all gears used in the Georges Bank Ecological Production unit defined by statistical areas"}
knitr::include_graphics("figures/dendrogram1.png")
```
Note: Low values of the agglomerative coefficient indicate tight clustering of gears types. Larger values indicate less well formed clusters.
